%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-0pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-0pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://users.soe.ucsc.edu/~chenzy}{\Large Ziyi Chen}} & Email : \href{mailto:zchen139@ucsc.edu}{zchen139@ucsc.edu}\\
  \href{http://users.soe.ucsc.edu/~chenzy}{http://users.soe.ucsc.edu/$\sim$chenzy} & Mobile : +(831)435-9183 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Master of Science in Computer Science}{Sep. 2016 -- Dec. 2017(expected)}
       \resumeItemListStart
        \resumeItem{GPA}{Overall 4.00/4.00}
        \resumeItem{Major courses}{Algorithm Analysis, Image Processing and Computer Vision, Data Visualization, Computational Model of Discourse and Dialog, Programming Languages}
        \resumeItemListEnd
    \resumeSubheading
      {College of Computer Science, Zhejiang University}{Hangzhou, China}
      {Bachelor of Engineering in Digital Media Technology}{Sep. 2012 -- June. 2016}
       \resumeItemListStart
        \resumeItem{GPA}{Overall: 3.82/4.00\qquad Major: 3.94/4.00}
        \resumeItem{Major courses:}{C Programming, Data Structure, Database System, Object-Oriented Programming, Operating System, Artificial Intelligence, Computer Graphics, Computer Game Programming}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hangzhou Aika Co.}{Hangzhou, China}
      {Web Development Intern}{Mar 2016 - Apr 2016}
      \resumeItemListStart
        \resumeItem{Font End}
          {Designed an web application using {\bf AJAX} which allows user to control real world game progress via smart phones.}
        \resumeItem{Back End}
          {Built the back end service with {\bf Node/Express} which receives commands from mobile phones and send signals to hardwares.}
      \resumeItemListEnd

    \resumeSubheading
      {State Key Lab of CAD\&CG, Zhejiang University}{Hangzhou, China}
      {Research Assistant}{Mar 2016 - Jun 2016}
      \resumeItemListStart
        \resumeItem{3D Rendering}
          {Implement an interactive high-performance 3D viewer based on {\bf WebGL} that renders house and furnitures in real time.}
        \resumeItem{Model Editor}
          {Built a 3D model editor with {\bf JavaScript}. Users are allowed to add/remove components (furnitures) into the 3D space. It also supports importing 3D components from CEMO(a 3D model format based on XML) files and exporting the whole model into common 3D formats.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Twitter Clustering and Topic Modeling}
      {A pipeline for tweets preprocessing was built based on {\it NLTK}, {\it CMU Twitter NLP} and {\it scikit-learn}. KMeans, LDA, BTM are used for clustering and topic modeling. A lexcion normlization algorithm was implemented.}
    \resumeSubItem{High Dynamic Range (HDR) Camera System}{
       A radiometric calibration based on {\it scikit-learn} was implemented to recover linear raw camera data. Three different algorithms were exploited to produce the combined image.
    }
    \resumeSubItem{Raspberry Pi Car}
      {An Android app and a Raspberry Pi server software. Socket connection is established between two ends to acheive remote control. An $A\ast$ algorithm were implemented to find shortest route and navigate.}
    \resumeSubItem{Image Completion}
      {Implemented a paper from SIGGRAPH 2005 based on {\it OpenCV}. Given user specified structure lines, the algorithm removes object that shields certain structure in the image. A dynamic programming algorithm and a belief propagation algorithm are used to complete line sturcture. }
    
  \resumeSubHeadingListEnd

\section{Skills}
  \resumeSubHeadingListStart 
    \resumeSubItem{Programming Languages}
      {C/C++, C\#, Java, JavaScript, HTML/CSS, Python, Haskell, SQL}
    \resumeSubItem{Frameworks:}
      {jQuery, Bootstrap, Node/Express, WebGL, OpenGL, OpenCV, Unity}
    \resumeSubItem{Softwares:}
      {Linux, Windows, Dreamweaver, Photoshop, Maya, Premiere}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
% \section{Awards}
%   \resumeSubHeadingListStart
%     \item{
%       {China Computer Federation Outstanding Undergraduate (99 in China) \hfill 2013}\\
%       {Third Prize for ACM ICPC in Zhejiang Province \hfill 2011}\\
%       {First Prize, National Olympiad in Informatics in Provinces \hfill 2008, 2009}
      
%     }
%   \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
